---
title: "Eating Out"
author: "Karen Gomez" 
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## There were two years in which the General Social Survey asked about the frequency of eating out.
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r, eval=FALSE}
GSS <-read.dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

### Graphical Results

```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")
```

Based on the frequency table above, which shows the volume of people who eat out and people who do not eat out for each racial group, we can see that about 950 white people eat out while about 200 do not. Meanwhile, about 200 black people eat out while about 100 do not. For the other racial groups, about 100 people eat out while about 50 do not. Putting this into percentages, 80% of white people eat out while 20% do not, meanwhile black and others have about the same percentages with 70% of the people eat out while 30% do not.

### Numerical Results

```{r}
table1 <- xtabs(~race + eatout,data=mydata)
rowPerc(table1)
colPerc(table1)
```

The numerical summary above shows the actual values of the percentages of people who eat out and do not eat out for each racial group. The data above confirms the estimations from the graphical results, and it shows that for white people, 83.13% eat out and 16.87% do not. Similar to the observations made previously, black people and others have a similar ratio of about 70% of people who eat out while 30% of people who do not. Furthermore, the table above shows that white people make up the majority of the people who claim that they eat out. Specifically, among the people who answered yes to eating out, 81.69% were white while 11.83% were black, and 6.48% were others. 


### Inferential Results

```{r}
chisq.test(table1)
chisqtestGC(table1)
```

Based on the chi-squared test above, the p-value determined is a small number which means that there is a difference between the frequency of eating out of the three racial groups. Therefore, we can reject the null hypothesis. To determine specifically which groups are different, another type of test will be conducted.

### Fisher Results

```{r}
fisherXY(mydata$race,mydata$eatout, printAll = TRUE)
```

Fisher's exact test is conducted to supplement the results of the Chi-squared test from before. Based on this test, which compared two groups at a time, we can see that there is a difference in-terms of frequency of eating out between white and black people as shown by the low p-value of about 1.183e-05,. Likewise, the frequency of eating out between white people and others is also different based on the low p-value of 0.0072. However, this test also shows that there is no difference between the frequency of eating out of black people or others given that the p-value is 0.599.

### Discussion and Conclusion




