---
title: "Eating Out"
author: "Karen Gomez" 
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## There were two years in which the General Social Survey asked about the frequency of eating out.
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r, eval=FALSE}
GSS <-read.dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

### Graphical Results

```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```

Based on the frequency table above, which shows the volume of people who eat out and people who do not eat out for each racial group, we can see that about 950 white people eat out while about 200 do not. Meanwhile, about 200 black people eat out while about 100 do not. For the other racial groups, about 100 people eat out while about 50 do not. Putting this into percentages, 80% of white people eat out while 20% do not, meanwhile black and others have about the same percentages with 70% of the people eat out while 30% do not.

### Numerical Results


### Inferential Results


### Fisher Results



### Discussion and Conclusion




